%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior Data Engineer} % Job title
    {Recharge.com} % Organization
    {Amsterdam, Netherlands} % Location
    {Nov. 2019 - Current} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        Responsible for data integration (Airflow, Python) from multiple sources mainly relational databases (Mysql RDS instances) and apis (Zendesk, Trustpilot, Contentful). Maintaining cloud infrastructure (AWS, Terraform), at a certain level, is also part of the job, like managing docker containers (ECR, ECS) as cloud filesystems (S3) and defining CI/CD pipelines (Gitlab). Finally, another responsibility is modelling datasets (Star Schema) in Data Warehouse (Exasol, Redshift).
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Business Intelligence Consultant} % Job title
    {Nórdica} % Organization
    {São Paulo, Brazil} % Location
    {Mar. 2019 - Nov. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        Responsible for data integration and visualization (Qlik Sense/View) in diverse projects, as well software migrations, from Qlik View to Qlik Sense.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Data Engineer \& Data Visualization Freelancer} % Job title
    {Cognitivo.ai} % Organization
    {Remote} % Location
    {Oct. 2018 - Oct. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        Working remotly on business intelligence projects, doing data integration (Python, Pentaho) and dashboards development (Tableau, Chartio).
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Bussiness Intelligence Analyst} % Job title
    {B2W Digital} % Organization
    {Rio de Janeiro, Brazil} % Location
    {Mar. 2016 - Apr. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        I have gathered requirements from stakeholders and transform them into products (Dashboards, Reports) for decision-making and acted as a facilitator to ensure business intelligence team flowed with no impediments, always garanting the product's quality. Also, I have done some data integration (PL/SQL, Pentaho) when needed.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Business Intelligence Analyst \& Database Administrator} % Job title
    {Sieve} % Organization
    {Rio de Janeiro, Brazil} % Location
    {Dec. 2014 - Feb. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
       I have taken care of kpi's and dashboards (Klipfolio), which provided information for business decision-making, also, supported the operational sector providing ad-hoc reports and administrated company's database (Postgresql, Mysql), performing preventive and corrective maintenance. Also, I have built a datawarehouse (Python, Pentaho, Exasol) for business data centralization.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Data Integration \& Data Cleansing Consultant} % Job title
    {Softtek} % Organization
    {Rio de Janeiro, Brazil} % Location
    {Feb. 2010 - Nov. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        I have worked on projects for large companies, gathering requirements and developing ETL procedures (Informatica Powercenter) and data cleansing (Informatica Data Quality).
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
